\documentclass{screenplay}

\title{pelagic venture}
\author{Yamani Álvarez}
\address{Computer Animation \\ Escuela Superior de Cómputo \\ yamalvarez23@gmail.com}
\agent{Norman Saucedo}

\begin{document}

\coverpage
\fadein

\extslug[day]{dive boat}
PILOT parks the boat. The ENGINE sound turns off slowly and the group stands up to check their equipment for the last time CHATTERING.
HELPER approaches each one of them briefly to assist. Some of the equipment CLINKS from the handling, there are also some VELCRO, ZIPPER and CLASPING sounds.

MARIO RINSES his dive mask with water from the bucket. ANA helps EDGAR to zip up his wetsuit. Then Edgar helps Ana to put on her dive vest. Mario also helps GABY to put on and adjust her vest.

Divemaster PAULINO gets equipped all by himself then FIN STEPS to the stern and faces towards the divers. 

\begin{dialogue}{paulino}
\paren{shouts}
Okay! Is everybody ready? Remember, one by one after me. Let’s go!
\end{dialogue}

Paulino steps onto the swim platform then jumps into the water which SPLASHES loudly.

Dive group follow orders and, in a line, enter the water SPLASHING one after the other, all signalling OK upwards towards the helper on the boat.

Helper and pilot both wave goodbye to the group of divers.

CUT TO:

\extslug[day]{ocean surface}
Ocean WAVES mildly rock the group of divers back and forth. The divers are scattered along the surface but begin to get closer to the divemaster. Gaby swims backwards towards the group and they all stop once they're fairly close together.

\begin{dialogue}{paulino}
\paren{shouting, counts divers and jokingly counts himself}
Get closer! Is everybody okay? One, two, three, four... five. Great! So you two are dive buddies?
\end{dialogue}

\begin{dialogue}{ana}
\paren{smiling}
Yes.
\end{dialogue}

Edgar also smiles and nods.

\begin{dialogue}{paulino}
\paren{pointing at them}
Okay then you will go first and then you two go second, OK? Ready to descend, everybody? Keep close to your buddies.
\end{dialogue}

Paulino deflates his vest with the button on his dive hose and starts to submerge as the AIR comes out and is slowly followed by the group who do the same.

As he instructed, Ana and Edgar follow his lead first and behind them go Mario and Gaby. Dive group submerges in pairs along the reel.

\extslug[day]{ocean floor}
Immeadiately BUBBLES and SCUBA BREATHING are heard. CAMERA at the bottom of the ocean TILTS up to down as the dive group submerges and they stop at the same level in which the divemaster is at. They all get on their knees on the seabed making an uneven circle formation.

\begin{dialogue}{paulino}
\paren{signalling - not talking, four times}
OK?
\end{dialogue}

\begin{dialogue}{ana}
\paren{signalling}
OK.
\end{dialogue}

\begin{dialogue}{edgar}
\paren{signalling}
OK.
\end{dialogue}

\begin{dialogue}{mario}
\paren{signalling}
OK.
\end{dialogue}

\begin{dialogue}{gaby}
\paren{signalling}
OK.
\end{dialogue}

CAMERA pans quickly but steadily as they sign in response.

\begin{dialogue}{paulino}
\paren{signalling}
This way.
\end{dialogue}

Paulino adopts optimus diving position, crosses his arms and starts swimming calmly. The dive group follows him in the same previusly arranged order, adopting ther positions as well.

\pagebreak

The dive group all navigates the ocean not long until they make a turn around the ocean landscape and they finally find the coral reef site which was awating them.

\extslug[day]{coral reef}
The colours of the scene starts changing from plain blue ocean water to all the colours of the rainbow from the coral reef. MIRACLE SOUND EFFECT and WIND CHIMES are played followed by LA MER song by Charles Trenet slowly rising volume, as well as BUBBLES and SCUBA BREATHING keep sounding all the time they're immerged at a lower volume.

A lot of different kinds of sea creatures are spotted. They are all coexisting peacefully as the coral reef sways very slowly from side to side due to the water currents and the fish swimming around it.

The dive group can recognise all the angelfish in different colours, there are yellow ones, white ones with orange coloured faces, pale blue ones, white ones with black stripes on them, gray ones and so on.

Then they get to see the famous clownfish which they've only seen on the finding nemo movie or documentaries so they are all very excited.

Other fish sightings include the following: bluestreak cleaner wrasse, foureye butterflyfish, sea goldie, blue caribbean tang, boxfish, ocean surgeon and damselfish among others. CAMERA slowly focuses on each kind.

The coral reef structure is made of sea anemone, stony coral and coral polyps seen in different sizes, shapes and colours including yellow, orange, pink, green, pale purple, tan, etc. There also are black sea urchins of different sizes kind of hidden amongst the reef.

The complete scenery looks majestic but also seems almost calm in a way. By the way in which all living creatures are minding their own business not even aknowledging the group of divers who solely came to see them and are just admiring the beauty and the harmony of this view.

Dive group floats above the coral reef looking around and moving forward quite slowly.

There is a medium size sea turtle which comes out from behind the coral reef structure and swims fastly upwards towards the ocean surface. Ana and Mario both follow its path upwards with their sight. The song that was continuously playing lowers volume slowly until it fully STOPS at the very moment when the turtle reaches the ocean surface. But the divemaster quickly has already kept going forward without paying it too much attention, so the group keeps on following his lead.

\pagebreak

Not long after, Paulino CLINKS his scuba tank with a long underwater noisemaker and pointer and looks back at the group of divers.

\begin{dialogue}{paulino}
\paren{signalling and pointing}
Look.
\end{dialogue}

The dive group follows the divemaster's gaze. There is a large eagle ray a bit far away, it is almost a shadow but its shape is still recogniseable. The eagle ray is swimming gracefully moving its fins up and down. This is the dive group's only focus until it gets far away enoguh that its silhouette is no longer visible.

At the time they're distracted just looking at the eagle ray as it faded away and then admiring the endless sea, there comes a nurse shark below them. Paulino CLINKS his scuba tank just in time for the group to see it as well.

They all look down as the nurse shark comes from the right side towards the divemaster. The shark after approaching Paulino from his right side then goes straight around Paulino's head area, then keeps swimming around the divemaster's left side of his body, all this at a very slow swimming pace.

The dive master seems as though he hadn't even noticed what happened around him. As if when the shark left his view, after it went towards his left side, it simply was out of his mind too.

After the shark goes around Paulino's fins it simply swims away going back from where the dive group came from. That is how the interaction between the dive group and the shark ends. An interaction that feelt even playful from the shark's side, as this is this type of shark's natural behaviour.

Edgar has his camera out and is fimling the whole scenery. GoPro TURN ON SOUND EFFECT can be heard muffled by the water. He pans his camera along the coral reef.

\begin{dialogue}{mario}
\paren{signalling - not talking}
Take a picture of me.
\end{dialogue}

Edgar nods and directs his camera at him. Mario crosses his arms and poses in front of the coral reef as his bubbles go up and clear the landscape for the picture. Ana comes swimming from the side and poses next to Mario. Edgar signals OK and then the three of them continue back to their siwimming positions.

\pagebreak

The dive group continues swimming a bit more. The landscape is now basically sand and water apart from some algae and black sea urchins scattered around but there are also a couple of starfish spotted laying around at the sea bottom.

Paulino gets on his knees on the sea bottom and instructs for the rest to do the same by signalling, so the dive group forms an uneven circle again where everybody is facing inwards.

\begin{dialogue}{paulino}
\paren{signalling}
Everybody ascend. OK?
\end{dialogue}

Paulino leads the way ascending towards the ocean surface and all the four other divers do the same practically at the same time. CAMERA at the bottom of the ocean TILTS down to up as the dive group ascends.

CUT TO:

\extslug[day]{ocean surface}
Ocean WAVES SPLASH and mildly rock the group of divers back and forth. All divers pump AIR to their vests with the button on their vest hose to inflate it. Smiles start to appear on their faces while they wipe their faces and noses with their hands.

\begin{dialogue}{paulino}
\paren{loud voice and smiling}
That was great! Wasn't it?
\end{dialogue}

\begin{dialogue}{mario}
\paren{smiles and shouts}
That shark was amazing!
\end{dialogue}

\begin{dialogue}{gaby}
\paren{tenderly and happy}
Aww! The turtle was so so cute!
\end{dialogue}

CHATTER slowly lowers in volume and LAUGHS get lower as well. CAMERA zooms out and the boat is seen a bit far away. All keep smiling and laughing. BEYOND THE SEA song by Bobby Darin covered by Kevin Spacey starts playing as the END CREDITS appear.

\fadeout
\theend

\end{document}
